Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
wip vobj

@@

>>>>

\input{nuobj}

@@

\begin{frame}{${\nu}Obj$}
A calculus for classes and objects which can have types as members. It can encode:
\begin{itemize}
\item Java's inner classes
\item virtual types
\item family polymorphism
\item essential aspects of ML-like module systems, including
\begin{itemize}
\item sharing constraints
\item higher-order functors
\end{itemize}
\end{itemize}
A basis for unifying concepts  in advaced object and module systems. Connections:
\begin{itemize}
\item Object = Module
\item Object type = Signature
\item Class = Method = Functor
\end{itemize}
\end{frame}

\begin{frame}{${\nu}Obj$: Syntax}
The terms in ${\nu}Obj$ denote objects or classes. They consist of
variables $x$ denoting objects, selections $t.l$, object creations
\mbox{$\newin{x \larrowc t}{u}$} defining an object $x$ of class $t$
whose scope is the term $u$, class templates $\cls{x: S \sep \tup d}$,
and mixin compositions $t \withsub{S} u$ denoting a class of self
type $S$ combined from two classes $t$ and $u$. A value is a variable
or a class template. A path is a variable followed by a possibly empty
sequence of selections.

The types in ${\nu}Obj$ consist of singleton types $p.\type$, type
selections $T\Tsel L$, record types $\obj{x \sep \tup D}$, compound
types $T \with U$, and class types $\cls{x: S \sep \tup D}$.
\begin{itemize}
\item TODO
\end{itemize}
\end{frame}
